The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-21 paper.tex
update

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  and assuming the disk and atmosphere is in pressure equilibrium,\
  we can write the steady-state gaseous density distributions,\
  confined in the total potential, of disk and the Galactic atmosphere as\
  \begin{equation}
     \rho(z)=
     \begin{cases}
     \displaystyle\rho_{\text{disk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{disk}}/m_{\text{p}}}\right] & \text{, if $|z| < z_{0}$}\\
     \\
     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right] & \text{, otherwise,}
     \end{cases}
  \end{equation}
  where $m_{\text{p}}$ is a proton mass,\
  $T_{\text{disk}}$ and $T_{\text{atmp}}$ is the temperature of the disk and the atmosphere,\
  $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
  of the disk and the atmosphere on the mid-plane $z=0$.

@@

  A crucial ingredient in our work is the clumpy ISM disk initialized by\
  the publicly available pyFC code
  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
  The spatial density distribution $\rho(\bold{x})$ of clumpy ISM obeys\
  the log-normal probability distribution in real space,\
  and the Kolmogorov power spectrum in the Fourier space.
  \begin{equation}
    D(k)=\int k^{2} \hat{\rho}(k)\hat{\rho}^{*}(k)dk \propto k^{-5/3},
  \end{equation}
  where $\hat{\rho}(k)$ is the Fourier transform of $\rho(\bold{x})$.

>>>>

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  and assuming the disk and atmosphere is in pressure equilibrium,\
  we can write the steady-state gaseous density distributions,\
  confined in the total potential, of disk and the Galactic atmosphere as\
  \begin{equation}
     \rho(z)=
     \begin{cases}
     \displaystyle\rho_{\text{disk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{disk}}/m_{\text{p}}}\right] & \text{, if $|z| < z_{0}$}\\
     \\
     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right] & \text{, otherwise,}
     \end{cases}
  \end{equation}
  where $m_{\text{p}}$ is the proton mass,\
  $T_{\text{disk}}$ and $T_{\text{atmp}}$ is the temperature of the disk and the atmosphere,\
  $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
  of the disk and the atmosphere on the mid-plane $z=0$.

@@

  A crucial ingredient in our work is the clumpy ISM disk initialized by\
  the publicly available pyFC code
  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
  The spatial density distribution $\rho(\bold{x})$ of clumpy ISM obeys\
  the log-normal probability distribution \citep{Berkhuijsen2008} with mean $\mu=1.3$ and dispersion $\sigma=0.13$ in real space,\
  and the power-law Kolmogorov spectrum
  \begin{equation}
    D(k)=\int k^{2} \hat{\rho}(k)\hat{\rho}^{*}(k)dk \propto k^{-5/3},
  \end{equation}
  where $\hat{\rho}(k)$ is the Fourier transform of $\rho(\bold{x})$.\
  The spectrum $D(k)$ with index $-5/3$ in the Fourier space has the cutoff wave number $k_{\text{min}}=375.0$,\
  corresponding to the average clump sizes of $\sim 20$ pc.
